### 2016-07-29 ClimaTrans/climatrans.Rmd
update

```{r}
wq95 <- function(x) {x <- x[is.finite(x)]; x <- x[x >= 1]; wq95 <- quantile(x,probs=0.95); wq95}
season<-5:10
fw <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wetfreq')
mu <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wetmean')
q95 <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wq95')
```

@@

@@

@@

```{r}
  load('climatrans.tx.rda')
  plot(as.4seasons(anomaly(climatrans.tx)),new=FALSE)
  for(i in 1:3) lines(trend(subset(as.4seasons(anomaly(climatrans.tx)),is=i)))
  grid()
```

>>>>

```{r}
wq95 <- function(x) {x <- x[is.finite(x)]; x <- x[x >= 1]; wq95 <- quantile(x,probs=0.95); wq95}
season<-5:10
fw <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wetfreq')
mu <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wetmean')
nd <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'nv')
q95 <- aggregate(subset(climatrans.pr,it=month.abb[season]),year,'wq95')
```

@@

```{r}
print(summary(coredata(pt)))
print(summary(coredata(fw*nd)))
print(summary(coredata(mu)))
```

@@

```{r}
## Retrieve the reanalysis from FTP
if (!file.exists("air.mon.mean.nc"))
  download.file('ftp://ftp.cdc.noaa.gov/Datasets/ncep.reanalysis.derived/surface/air.mon.mean.nc',
              destfile = 'air.mon.mean.nc')
if (!file.exists("slp.mon.mean.nc"))
  download.file('ftp://ftp.cdc.noaa.gov/Datasets/ncep.reanalysis.derived/surface/slp.mon.mean.nc',
              destfile = 'slp.mon.mean.nc')
```

@@

```{r}
  load('climatrans.tx.rda')
  plot(as.4seasons(anomaly(climatrans.tx)),new=FALSE)
  for(i in 1:3) lines(trend(subset(as.4seasons(anomaly(climatrans.tx)),is=i)))
  grid()
  print(summary(coredata(climatrans.tx)))
```
